% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper, 12pt]{article}
\usepackage{eurosym}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage[backend=biber,style=authoryear,maxbibnames=99]{biblatex}
\addbibresource{cv.bib}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=0pt,labelsep=0.6em,align=left}
% Set your name here
\def\name{Giacomo M. Anastasia}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  left=1in,
  right=1in,
  top=1.1in,
  bottom=1.1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.15in}


\begin{minipage}{0.5\linewidth}
 Columbia Business School \\
 590-8 Kravis Hall \\
   $665$ West $130^{th}$ Street \\
   New York, 10027 NY
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{tabular}{ll}
    Phone: & (+39) 342 3670636 \\
    & (+1) 332 269-8155 \\
    Email: & \href{mailto:giacomo.anastasia@columbia.edu}{\tt giacomo.anastasia@columbia.edu} 
  \end{tabular}
\end{minipage}
\smallskip
\section*{Education}
\begin{itemize} 
  \item[] \textbf{PhD in Economics, Columbia University}. Business Economics track. 2024-present.
  \item[] \textbf{MSc in Economics and Social Sciences, Bocconi University} (\textit{cum laude}).  2020-2023.
  \item[] \textbf{BA in Philosophy, Politics \& Economics, Ca' Foscari University} (\textit{cum laude}). 2017-2020.
\end{itemize}

\section*{Research}
\nocite{*}

\subsection*{Working paper}
\printbibliography[keyword=wp,heading=none]

\subsection*{Book chapter}
\printbibliography[keyword=chapter,heading=none]

\smallskip

\section*{Activities and experience}
\begin{itemize}
    \item[] \textit{Scientific Collaborator}. \href{https://www.festivalinternazionaledelleconomia.com/en/}{Turin International Festival of Economics}. 2021-present.
    \item[]  \textit{Research Assistant} for Cristóbal Otero. Columbia Business School. 2025-present. 
\item[]  \textit{Research Assistant} for Tito Boeri. Bocconi University. 2022-2024. 
\item[]  \textit{Research Assistant} for Francesco Decarolis. Bocconi University. 2022-2023. 
\item[]  \textit{Teaching Assistant}. Labor Economics, prof. Tito Boeri. Bocconi University. 2022-2024. 
\item[]  \textit{Research Fellow}. Ca' Foscari Economics Department. 2021.
\end{itemize}
\smallskip
\section*{Policy and other writings}
\begin{enumerate}
\item  Book reviews, \href{https://www.rivistaeco.com}{Rivista Eco}, monthly column with Giovanni Brocca (NYU Stern). 2024-present.
    \item  "What to Do About Ukraine's Brain Drain", with T. Boeri, \href{https://www.project-syndicate.org/commentary/ukraine-brain-drain-rebuilding-human-capital-by-giacomo-anastasia-and-tito-boeri-2023-11}{Project Syndicate}. Also published in \href{https://kyivindependent.com/opinion-what-to-do-about-ukraines-brain-drain/}{The Kyiv Independent} and \href{https://www.businesstimes.com.sg/opinion-features/what-do-about-ukraines-brain-drain}{The Business Times}. 2023.
    \item  "Qualificazione delle stazioni appaltanti, il Codice 36 non premia chi rispetta tempi e costi del contratto", \href{https://diarionuoviappalti.it/il-codice-36-non-premia-le-stazioni-appaltanti-che-rispettano-tempi-e-costi-del-contratto/}{DiarioNuoviAppalti} (interview). 2023.
    \item  "The labour market in Ukraine: Rebuild better", with T. Boeri, M. Kudlyak and O. Zholud, \href{https://cepr.org/voxeu/columns/labour-market-ukraine-rebuild-better}{VoxEU}. Also published in \href{https://voxukraine.org/en/the-labour-market-in-ukraine-rebuild-better/}{VoxUkraine}. 2023.
    \item  "Il dopoguerra dell'Ucraina", with T. Boeri, \href{https://www.lavoce.info/archives/99340/il-dopoguerra-dellucraina/}{laVoce.info}. 2022.

\end{enumerate}
\smallskip
\section*{Fellowship and Scholarships}
\begin{itemize}
\item[]  Fellow, Fondazione Ing. Rodolfo Debenedetti. 2023-present.
\item[]  Ermenegildo Zegna Founder's Scholarship (\$10k). 2024.
\item[] Bonaldo Stringher Scholarship (\textit{particolarmente meritevole}), Bank of Italy. 2024.
\item[]  Fulbright Scholarship (\textit{declined}). 2024.
\item[]  Bishop's University Prize for Excellence in Economics Research. 2020.
\end{itemize}
\smallskip
\section*{Languages}
Italian (native), English (fluent), French (intermediate).
\vspace{2cm}
\begin{center}
  Last updated: February 2026
\end{center}
 \thispagestyle{empty}
\end{document}